\sysfull

### 2018-04-15 paper/hwswsetup.tex

We evaluated \sys using six benchmarks summarized in Table~\ref{table:benchmark_table}, with their implementation is available via~\cite{coala_website}. Five originate from the MiBench testing suite~\cite{mibench,hicks_mibench2_2016}: three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) were implemented by Chain~\cite{chain} and Alpaca~\cite{alpaca}, while two (\textbf{dijkstra}, \textbf{fft}) are added as new. The final one (\textbf{sort}) has been written from scratch. \todo{justify the selection of these benchmarks}{Przemek, Carlo, Amjad, Brandon}

>>>>

We evaluated \sys using six benchmarks summarized in Table~\ref{table:benchmark_table}, with their implementation is available via~\cite{coala_website}. Five benchmarks originate from the MiBench testing suite~\cite{mibench,hicks_mibench2_2016}: three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) were already implemented by Chain~\cite{chain} and Alpaca~\cite{alpaca}, while two (\textbf{dijkstra}, \textbf{fft}\footnote{Specifically, we re-implemented FFT based on the TI's accelerated FFT library~\cite{}.\todo{add reference}{Przemek}}) are added as new. The final one (\textbf{sort}) has been written from scratch. \todo{justify the selection of these benchmarks}{Przemek, Carlo, Amjad, Brandon}

### 2018-04-15 paper/implementation.tex

\textbf{Execution.} The application control is passed to \sys's execution manager by calling \texttt{COALA\_RUN} at the end of the main function. A high-level state machine of the execution manager is depicted in Figure~\ref{fig:coala_state_machine} \todo{Draw a figure reflecting the following description}{Sinan, Carlo}. Upon reboot, the coalescing target is initialized according to the coalescing strategy. Then, the ultimate commit is resumed, in case the last power failure occurred during this operation. The shadow buffer list is cleared, and the metadata of the volatile buffer is initialized. The pointer to the last coalescing task is recalled from non-volatile memory. Before running, Coala checks whether there is any partial execution to resume, in which case the volatile state, including the PC, is restored. Otherwise, coalescing starts: the current budget is replenished; tasks are run, the history is increased and the current budget is decreased; when the latter is zero, coalescing stops, the pointer to the next task is saved and the (intermediate) commit starts. Coalescing resumes after the ultimate commit is complete and the target is updated based on the coalescing strategy. \todo{Go over keywords (coalescing target, current budget, commit phases etc.) and make them consistent with the rest of the paper}{Amjad, Carlo}

>>>>

\noindent \textbf{Execution.} The application control is passed to \sys's execution manager by calling \texttt{COALA\_RUN} at the end of the main function. A high-level state machine of the execution manager is depicted in Figure~\ref{fig:coala_state_machine} \todo{Draw a figure reflecting the following description}{Sinan, Carlo}. Upon reboot, the coalescing target is initialized according to the coalescing strategy. Then, the second phase of the commit is resumed, in case the last power failure occurred during this operation. The shadow buffer list is cleared, and the metadata of the volatile buffer is initialized. The pointer to the last coalescing task is recalled from non-volatile memory. Before running, \sys checks whether there is any partial execution to resume, in which case the volatile state, including the program counter, is restored. Otherwise, coalescing starts: the current budget is replenished; tasks are run, the history is increased and the current budget is decreased; when the latter is zero, coalescing stops, the pointer to the next task is saved and the commit phase starts. Coalescing resumes after commit phase two ends and the target is updated based on the coalescing strategy. \todo{Go over keywords (coalescing target, current budget, commit phases etc.) and make them consistent with the rest of the paper}{Amjad, Carlo}
